\documentclass[format=acmsmall, review=false, screen=true]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}


% Metadata Information
\acmJournal{CSUR}
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\acmYear{0}
\acmMonth{0}
\copyrightyear{2017}
%\acmArticleSeq{9}

% Copyright
%\setcopyright{acmcopyright}
% \setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
\acmPrice{0.00}

% DOI
\acmDOI{0000001.0000001}

% Paper history
\received{February 2007}
\received[revised]{March 2009}
\received[accepted]{June 2009}

\newcommand{\massa}{{\large \textsc{mass}}}
\newcommand{\mass}{{\large \textsc{mass}}}
\newcommand{\figgus}{{\large \textsc{figgus}}}

% Document starts
\begin{document}
% Title portion. Note the short title for running heads 
\title[Music in digital audio]{Musical elements in the discrete-time representation of sound}  
\author{Renato Fabbri}
% \orcid{1234-5678-9012-3456}
\affiliation{%
  \institution{University of S\~ao Paulo}
  \department{Institute of Mathematics and Computer Sciences}
  \streetaddress{Avenida Trabalhador S\~ao Carlense, 400 - Centro}
  \city{S\~ao Carlos}
  \state{SP}
  \postcode{13566-590}
  \country{Brazil}}
\author{Vilson Vieira da Silva Junior}
\affiliation{%
  \institution{Cod.ai}
%  \department{Research and Development}
  \city{Berlin}
  \state{BE}
  \postcode{???}
  \country{DE}
}
\author{Ant\^onio Carlos Silvano Pessotti}
\affiliation{%
  \institution{Universidade Metodista de Piracicaba}
  \department{??}
  \city{Piracicaba}
  \state{SP}
  \postcode{???}
  \country{Brazil}}
\author{D\'ebora Cristina Corr\^ea}
\affiliation{%
  \institution{University of Western Australia}
  \department{??}
  \city{Piracicaba}
  \state{SP}
  \postcode{???}
  \country{AU}
  }
\author{Osvaldo N. Oliveira Jr.}
\affiliation{%
  \institution{University of S\~ao Paulo}
  \department{S\~ao Carlos Institute of Physics}
  \streetaddress{Avenida Trabalhador S\~ao Carlense, 400 - Centro}
  \city{S\~ao Carlos}
  \state{SP}
  \postcode{13566-590}
  \country{Brazil}
  }

\begin{abstract}
The representation of basic elements of music - such as notes,
ornaments and intervals - in terms of discrete audio
signals is often used in software for music creation and design.
Nevertheless, there is no unified approach that relates these elements to the discrete samples of digitized sound.
In this article, each musical element is related by equations and algorithms to the discrete-time samples of sounds,
and each of these relations are implemented in scripts within a software toolbox,
referred to as \massa\ (Music and Audio in Sample Sequences).
The toolbox also includes this article and every script necessary to render the images
and musical examples, pieces and albums, which adds to the educational and artistic uses.
The fundamental element, the musical note with duration, volume, pitch and timbre,
is related quantitatively to characteristics of the digital signal.
Internal variations of a note, such as tremolos, vibratos and spectral fluctuations,
are also considered, which enables the synthesis of notes inspired by real instruments and new sonorities.
With this representation of notes, resources are provided for the generation of higher scale musical structures,
such as rhythmic meter, pitch intervals and cycles.
This framework enables precise and trustful scientific experiments and is useful for education and art.
The efficacy of \massa\ is confirmed by the synthesis of small musical pieces using basic notes,
elaborated notes and notes in music, which reflects the organization of the toolbox and of this article.
It is possible to synthesize whole albums through collage of the scripts and settings specified by the user.
With the open source paradigm, the toolbox can be promptly scrutinized,
expanded in co-authorship processes and used with freedom by musicians, engineers and other interested parties.
In fact, \massa\ has already been employed by external users for diverse purposes which include music production,
artistic presentations, psychoacoustic experiments and computer language diffusion where the appeal of audiovisual artifacts is exploited for education.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
  <ccs2012>
    <concept>
      <concept_id>10010405.10010469.10010475</concept_id>
      <concept_desc>Applied computing~Sound and music computing</concept_desc>
      <concept_significance>500</concept_significance>
    </concept>
    <concept>
      <concept_id>10010147.10010341.10010342.10010343</concept_id>
      <concept_desc>Computing methodologies~Modeling methodologies</concept_desc>
      <concept_significance>300</concept_significance>
    </concept>
    <concept>
      <concept_id>10002944.10011122.10002945</concept_id>
      <concept_desc>General and reference~Surveys and overviews</concept_desc>
      <concept_significance>300</concept_significance>
    </concept>
    <concept>
      <concept_id>10002944.10011122.10002946</concept_id>
      <concept_desc>General and reference~Reference works</concept_desc>
      <concept_significance>300</concept_significance>
    </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Applied computing~Sound and music computing}
\ccsdesc[300]{Computing methodologies~Modeling methodologies}
\ccsdesc[300]{General and reference~Surveys and overviews}
\ccsdesc[300]{General and reference~Reference works}

%
% End generated code
%


\keywords{music, acoustics, psychophysics, digital audio, signal processing}


\thanks{This work is supported by FAPESP and CNPq.}


\maketitle

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{R. Fabbri et al.}

\input{body}


\end{document}
